Figures and tables for paper

### 2021-12-11 analysis/04_figs-tables.Rmd
Finished contrasts through hypothesis 4b

To formally answer the hypotheses, we compute contrasts of the marginal posteriors. First, we need the intercept-only draws and associated levels.

@@

# Join level and covariate labels to draws
draws_intercept <- draws_intercept %>% 
  left_join(level_lookup, by = "i")
```

@@

```{r contrasts-hypothesis01}
# Compute the contrasts
contrasts <- tibble(
  amnesty = draws_intercept %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws_intercept %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws_intercept %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws_intercept %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "oxfam - amnesty" = oxfam - amnesty,
    "oxfam - greenpeace" = oxfam - greenpeace,
    "red cross - amnesty" = red_cross - amnesty,
    "red cross - greenpeace" = red_cross - greenpeace,
  )

# Plot the contrasts
contrasts %>%
  pivot_longer("oxfam - amnesty":"red cross - greenpeace", names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace. However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam. In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International. This might be because the population we sampled from was specifically in the United States, where Oxfam and Amnesty may be less well known.

@@

```{r contrasts-hypothesis02a}
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts <- tibble(
  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer("crackdown - friendly":"criticized - friendly", names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.

@@

# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "criticized oxfam - criticized amnesty" = 
      (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized oxfam - criticized greenpeace" = 
      (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "criticized red cross - criticized amnesty" = 
      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized red cross - criticized green peace" = 
      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "crackdown oxfam - crackdown amnesty" = 
      (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown oxfam - crackdown greenpeace" = 
      (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
    "crackdown red cross - crackdown amnesty" = 
      (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown red cross - crackdown greenpeace" = 
      (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized oxfam - criticized amnesty":"crackdown red cross - crackdown greenpeace", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions. The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "environment - emergency":"refugee relief - emergency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors appear to be sensitive to NGO issue area when they are considering to donate. Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations. While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, although this is not significantly different from their likelihood of donating for environmental causes. In other words, refugee relief appears to be as contentious as environment.

@@

# Reference Level = Emergency Response
# Compute the contrasts
contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_human_rights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_human_rights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
    "criticized emergency - criticized environment" = 
      (criticized) - (criticized + environment + criticized_environment),
    "criticized emergency - criticized human rights" = 
      (criticized) - (criticized + human_rights + criticized_human_rights),
    "crackdown emergency - crackdown environment" = 
      (crackdown) - (crackdown + environment + crackdown_environment),
    "crackdown emergency - crackdown human rights" = 
      (crackdown) - (crackdown + human_rights + crackdown_human_rights),
    "criticized refugee relief - criticized environment" = 
      (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
    "criticized refugee relief - criticized human rights" = 
      (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_human_rights),
    "crackdown refugee relief - crackdown environment" = 
      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
    "crackdown refugee relief - crackdown human rights" = 
      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_human_rights)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized emergency - criticized environment":"crackdown refugee relief - crackdown human rights", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive. However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative. Here the issue area itself matters far more than the relationship with the host government.

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "wealthy donors - small donors":"government grants - small donors", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.

@@

# Reference Level = Funded primarily by many small private donations
# Compute the contrasts
contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  "criticized small donors - criticized wealthy donors" = 
    (criticized) - (few_wealthy_private_donors + criticized + criticized_wealthydonors),
  "criticized small donors - criticized government grants" = 
    (criticized) - (government_grants + criticized + criticized_grants),
  "crackdown small donors - crackdown wealthy donors" = 
    (crackdown) - (few_wealthy_private_donors + crackdown + crackdown_wealthydonors),
  "crackdown small donors - crackdown government grants" = 
    (crackdown) - (government_grants + crackdown + crackdown_grants)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized small donors - criticized wealthy donors":"crackdown small donors - crackdown government grants", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

All of the contrasts are positive and significant, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    emergency_humanrights_wealthydonors:refugee_environment_grants, 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices
# Pull the relevant posterior draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds"))

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
# Lower order interaction draws
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
draws_5c <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
draws_5d <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanrights_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

>>>>

To formally answer the hypotheses, we compute contrasts of marginal posteriors. First, we need the intercept-only draws and associated levels.

@@

# Join levels and labels to draws
draws_intercept <- draws_intercept %>% 
  left_join(level_lookup, by = "i")
```

@@

```{r contrasts-hypothesis01}
# Compute the contrasts
contrasts <- tibble(
  amnesty = draws_intercept %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws_intercept %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws_intercept %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws_intercept %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "oxfam - amnesty" = oxfam - amnesty,
    "oxfam - greenpeace" = oxfam - greenpeace,
    "red cross - amnesty" = red_cross - amnesty,
    "red cross - greenpeace" = red_cross - greenpeace
  )

# Plot the contrasts
contrasts %>%
  pivot_longer("oxfam - amnesty":"red cross - greenpeace", names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace, holding every other attribute constant. However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam. In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International. This might be because the population we sampled from was specifically in the United States, where Oxfam and Amnesty may be less well known.

@@

```{r contrasts-hypothesis02a}
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts <- tibble(
  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull(),
  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer("crackdown - friendly":"criticized - friendly", names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, holding every other attribute constant, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.

@@

# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  # Attribute levels
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 2b
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "criticized oxfam - criticized amnesty" = 
      (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized oxfam - criticized greenpeace" = 
      (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "crackdown oxfam - crackdown amnesty" = 
      (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown oxfam - crackdown greenpeace" = 
      (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
    "criticized red cross - criticized amnesty" = 
      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized red cross - criticized greenpeace" = 
      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "crackdown red cross - crackdown amnesty" = 
      (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown red cross - crackdown greenpeace" = 
      (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized oxfam - criticized amnesty":"crackdown red cross - crackdown greenpeace", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions, holding every other attribute constant. The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "environment - emergency":"refugee relief - emergency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors appear to be sensitive to NGO issue area when they are considering to donate. Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations, holding every other attribute constant. While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs relative to emergency response, although this is not significantly different from their likelihood of donating for environmental causes with the same reference. In other words, refugee relief appears to be as contentious as environmental issues.

@@

# Reference Level = Emergency Response
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  # Attribute levels
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 3b
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_human_rights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_human_rights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "environment - emergency" = environment,
    "human rights - emergency" = human_rights,
    "refugee relief - emergency" = refugee_relief,
    "criticized environment - criticized emergency" = 
      (criticized + environment + criticized_environment) - (criticized),
    "criticized human rights - criticized emergency" = 
      (criticized + human_rights + criticized_human_rights) - (criticized),
    "criticized refugee relief - criticized emergency" = 
      (criticized + refugee_relief + criticized_refugee) - (criticized),
    "crackdown environment - crackdown emergency" = 
      (crackdown + environment + crackdown_environment) - (crackdown),
    "crackdown human rights - crackdown emergency" = 
      (crackdown + human_rights + crackdown_human_rights) - (crackdown),
    "crackdown refugee relief - crackdown emergency" = 
      (crackdown + human_rights + crackdown_human_rights) - (crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "environment - emergency":"crackdown refugee relief - crackdown emergency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

When NGOs are criticized by the government, we see the same pattern as before, with emergency response being most preferred followed by human rights, environment, and refugee relief, holding every other attribute constant. However, we do not see an increase in likelihood to donate relative to an emergency response NGO being criticized. However, when NGOs are under crackdown by the government, we see that human rights, environment, and refugee relief all increase in their likelihood relative to an emergency response NGO under crackdown. In fact, both human rights and refugee relief NGOs under crackdown are indistinguishable from an emergency response NGO under crackdown in terms of propensity to donate.

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "wealthy donors - small donors":"government grants - small donors", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants, holding every other attribute constant, with government grants preferred to a small handful of wealthy donors relative to numerous small private donors.

@@

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  "wealthy donors - small donors" = few_wealthy_private_donors,
  "government grants - small donors" = government_grants,
  "criticized wealthy donors - criticized small donors" = 
    (few_wealthy_private_donors + criticized + criticized_wealthydonors) - (criticized),
  "criticized government grants - criticized small donors" = 
    (government_grants + criticized + criticized_grants) - (criticized),
  "crackdown wealthy donors - crackdown small donors" = 
    (few_wealthy_private_donors + crackdown + crackdown_wealthydonors) - (crackdown),
  "crackdown government grants - crackdown small donors" = 
    (government_grants + crackdown + crackdown_grants) - (crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "wealthy donors - small donors":"crackdown government grants - crackdown small donors", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

There is no significant increase in willingness to donate to NGOs facing government criticism or crackdown that are funded primarily by small private donors, holding every other attribute constant. The same pattern holds with small private donors most preferred, followed by government grants and wealthy donors, with their relative importance held constant.

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    emergency_humanrights_wealthydonors:refugee_environment_grants, 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

holding every other attribute constant

@@

```{r contrasts-hypothesis05a}
# Pull the posterior draws for organizational practices
# Pull the relevant posterior draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds"))

@@

# Plot the contrasts
contrasts %>%
  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r contrasts-hypothesis05b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r contrasts-hypothesis05c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
# Lower order interaction draws
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r contrasts-hypothesis05d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

```{r contrasts-hypothesis05e}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
draws_5c <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
draws_5d <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

@@

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_sd_emergency_environment_criticized:fin_sd_refugee_humanrights_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")
